---
title: "LogisticRegression"
author: "Mark Albrecht"
date: "November 22, 2015"
output: html_document
---

Below is the analysis source code and data supporting the publication **Forced-air warming linked to periprosthetic total joint replacement infections**.  This is a R-markdown document, so it can be run directly in the R-Console to reproduce the results.

####Raw Data

The raw infection data by hospital is: 

```{r}
data <- data.frame(Hospital = c("Center1","Center1","Center2","Center2","Center3","Center3","Combined","Combined","PublicationRef","PublicationRef"),Device = c("CFW","FAW","CFW","FAW","CFW","FAW","CFW","FAW","CFW","FAW"),Infections = c(2,6,0,4,2,6,4,16,10,22),NonInfections = c(675,382,218,171,192,376,1085,929,1087,655))

summary(data)
```


The fitted models for each center and the pooled results are done using a Haldane correction, which corresponds to adding 1/2 a count to all cells prior to model fitting.  One can argue the proper correction method for sparse data, but the haldane add 1/2 psuedo count prior is one of the most common and, therefore, will be applied here to each center.  The reason we are applying a corrrection method across all of these center specific analyses and the pooled result, is that they have counts below 5 in one of the contingency table cells and as such are considered to be "sparse".  This is a conservative estimation method that will understate the odds and significance versus methods that assume no prior and use the exact counts.

```{r}
dataHaldane <- data
dataHaldane[,c("Infections","NonInfections")] <- dataHaldane[,c("Infections","NonInfections")] + 0.5

###group the counts
counts <- cbind(dataHaldane$Infections,dataHaldane$NonInfections)
hospitals <- c("Center1","Center2","Center3","Combined","PublicationRef")
i=1
models <- list()
null <- list()
result <- data.frame()
for(i in 1:length(hospitals)){
  center <- hospitals[i]
  idx <- dataHaldane$Hospital == center
  tmpdata <- dataHaldane[idx,]
  countstmp <- cbind(tmpdata$Infections,tmpdata$NonInfections)
  models[[i]] <- glm(countstmp~tmpdata$Device,family=binomial)
  null[[i]] <- glm(countstmp~1,family=binomial)
  #summary(models[[i]])
  #summary(null[[i]])
  Chisq <- anova(models[[i]],null[[i]],test="Chisq")
  print(Chisq)
  OR <- coef(models[[i]])[2]
  Variance <- vcov(models[[i]])[2,2]
  LCL <- OR + qnorm(0.05/2)*sqrt(Variance)
  UCL <- OR + qnorm(1-0.05/2)*sqrt(Variance)
  result <- rbind(result,data.frame(Hospital = center,
                                     Device = names(OR),
                                     LCL = exp(LCL),
                                     OR = exp(OR),
                                     UCL = exp(UCL),
                                     Pvalue= Chisq[2,5]))
  
}

print(result)


```





